Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-06 popl24/hyperprop.tex
checkpoint

As we've discussed in our section on Related Work
(\ref{section-related}), previous authors have noted connections
between the traditional formulation of the MPC security model- aka the
simulator security model- and hyperproperty-style formulations of
program trace behavior \cite{XXX} including probabilistic
noninterference. This formulation of hyperproperties that are at least
sound with respect to simulator security bridges a conceptual gap
between foundational approaches to security, and also motivates and
supports automated analysis \cite{XXX}.

@@

\subsection{Passive Security and the Real/Ideal Model}
\label{section-hyperprop-passive}
Here we briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{XXX}.
In this paper, we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

\subsection{Probabilistic Noninterference}
\label{section-hyperprop-ni}
Previous work has noted
relations between probabilistic noninterference and security
properties such as memory trace obliviousness \cite{XXX} and passive
security \cite{XXX}. And above (Section \ref{section-pmf-examples}) we
have demonstrated that our basic encryption scheme enjoys a noninterference
property. To formulate probabilistic noninterference in
our setting we begin by defining low equivalence of memories.
\begin{definition}[Memory Low Equivalence]
  Given $\store^1$ and $\store^2$ with $\dom(\store^1) = \dom(\store^2) = X$,
  we write $\store^1 =_C \store^2$ iff $\store^1_{X_C} = \store^2_{X_C}$.
\end{definition}
Now, we can define probabilistic noninterference as a property of
programs ensuring that low-equivalent initial memories produce
the same low-observable trace (i.e., corrupt views) \emph{with the
same probability}. 
\begin{definition}[Probabilistic Noninterference]
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, we say that
  $\prog$ satisfies \emph{probabilistic noninterference} iff for all
  $\store_1, \store_2 \in \mems(S)$:
  $$\store_1 =_C \store_2 \implies
    \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}$$
\end{definition}

@@

Probabilistic noninterference can also be restated to formally capture a
basic intuition that noninterfering programs do not provide
the adversary with any clues about honest secrets through corrupt
views, as in the following Lemma. This is similar to asserting that
adversarial knowledge is not increased by the execution of a program as in formulations
of so-called gradual release \cite{XXX}. 
\begin{lemma}
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, 
  $\prog$ satisfies probabilistic noninterference iff for all
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{S_C}})}{S_H} =
    \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
\end{lemma}

>>>>

As we've discussed in our section on Related Work
(\ref{section-related}), previous authors have noted connections
between the traditional formulation of the MPC security model- aka the
simulator security model- and hyperproperty-style formulations of
program trace behavior \cite{8429300,wysstar} including probabilistic
noninterference. This formulation of hyperproperties that are at least
sound with respect to simulator security bridges a conceptual gap
between foundational approaches to security, and also motivates and
supports automated analysis.

@@

\subsection{Passive Security and the Real/Ideal Model}
\label{section-hyperprop-passive}
Here we briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{evans2018pragmatic}.
In this paper, we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

\subsection{Probabilistic Noninterference}
\label{section-hyperprop-ni}
Previous work has noted
relations between probabilistic noninterference and security
properties such as memory trace obliviousness \cite{darais2019language} and passive
security \cite{barthe2019probabilistic}. And above (Section \ref{section-pmf-examples}) we
have demonstrated that our basic encryption scheme enjoys a noninterference
property. To formulate probabilistic noninterference in
our setting we begin by defining low equivalence of memories.
\begin{definition}[Memory Low Equivalence]
  Given $\store^1$ and $\store^2$ with $\dom(\store^1) = \dom(\store^2) = X$,
  we write $\store^1 =_C \store^2$ iff $\store^1_{X_C} = \store^2_{X_C}$.
\end{definition}
Now, we can define probabilistic noninterference as a property of
programs ensuring that low-equivalent initial memories produce
the same low-observable trace (i.e., corrupt views) \emph{with the
same probability}. 
\begin{definition}[Probabilistic Noninterference]
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, we say that
  $\prog$ satisfies \emph{probabilistic noninterference} iff for all
  $\store_1, \store_2 \in \mems(S)$:
  $$\store_1 =_C \store_2 \implies
    \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}$$
\end{definition}

@@

Probabilistic noninterference can also be restated to formally capture a
basic intuition that noninterfering programs do not provide
the adversary with any clues about honest secrets through corrupt
views, as in the following Lemma. This is similar to asserting that
adversarial knowledge is not increased by the execution of a program as in formulations
of so-called gradual release \cite{4223226}. 
\begin{lemma}
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, 
  $\prog$ satisfies probabilistic noninterference iff for all
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{S_C}})}{S_H} =
    \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
\end{lemma}
